---
title: "Comparing_models"
output: html_document
date: "2023-09-18"
---

```{r}
library(readr)
library(dplyr)
library(forcats)
library(lme4)
library(glmnet)
library(optimx)

```

```{r}
df_nonmerged <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/Non_Merged/Sample/temp/Sample_10000_manual.csv")
df_merged <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/Merged/pr_merged_final_April_2023.csv")
df_comp <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/pr_final_April_2023.csv")
df_TSE <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Reza's Dataset/TSE paper/2020-TSE-Developers-Perceptible-Ethnicity-and-PR-evaluation-main/Dataset/pull_requests.csv")
```

```{r}
df_TSE <- df_TSE %>%
  distinct(pr_id, .keep_all = TRUE)

df_nonmerged <- df_nonmerged %>%
  distinct(pr_id, .keep_all = TRUE)
```

```{r}
df_nonmerged <- left_join(df_nonmerged, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)
```

```{r}
df_merged <- left_join(df_merged, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)

df_comp <- left_join(df_comp, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)
```

```{r}
df_nonmerged <- df_nonmerged %>%
  select(-c(`Unnamed: 0`, pr_id, api_url, url, pr_url, prs_white, prs_api, prs_black, prs_hispanic, pri_white, pri_black, pri_api, pri_hispanic , pr_api_url, author_desc_body, closer_id, comments, created_at, closed_at))


df_merged <- df_merged %>%
  select(-c(`Unnamed: 0`, pr_id, api_url, url, pr_url, prs_white, prs_api, prs_black, prs_hispanic, pri_white, pri_black, pri_api, pri_hispanic , pr_api_url, author_desc_body, comments, created_at, closed_at))


df_comp <- df_comp %>%
  select(-c(`Unnamed: 0`, pr_id, api_url, url, pr_url, prs_white, prs_api, prs_black, prs_hispanic, pri_white, pri_black, pri_api, pri_hispanic , pr_api_url, author_desc_body, comments, created_at, closed_at))

```

```{r}
df_comp <- df_comp %>%
  select(-c(closer_id))
```

# Building the model in rejected categories
for one rejected category against all the other categories. here for testing we are going to use 

```{r}
# Create a copy of df_nonmerged
df_nonmerged_encoded <- df_nonmerged

# Define encoding for 'manual_analysis' column
encoding <- c(
  'Quality' = 0, 'Successful' = 0, 'Unnecessary' = 1, 'No reason' = 0,
  'Resolved' = 0, 'Replaced' = 0, 'Duplicate' = 0, 'Stale' = 0,
  'Merge Conflict' = 0, 'Chaotic' = 0, 'Not PR' = 0
  
)

# Map the encoding to 'manual_analysis' and convert to integer
df_nonmerged_encoded$manual_analysis <- as.integer(factor(df_nonmerged_encoded$manual_analysis, levels = names(encoding)))
df_nonmerged_encoded$manual_analysis <- encoding[df_nonmerged_encoded$manual_analysis]

# Replace missing values with 0 in selected columns
df_nonmerged_encoded[is.na(df_nonmerged_encoded)] <- 0

# Encode categorical columns using forcats
categorical_cols <- c(
  'author_id', 'author_eth', 'author_country', 'author_continent',
  'closer_eth', 'prs_eth_8', 'prs_eth_7', 'prs_eth_9',
  'prs_eth_diff', 'prs_eth_diff_2', 'closer_country', 'status'
)

for (col in categorical_cols) {
  df_nonmerged_encoded[[col]] <- as.integer(factor(df_nonmerged_encoded[[col]]))
}

```

```{r}
table(df_nonmerged_encoded$manual_analysis)
```
```{r}
# Define the columns with '\\N' values
columns_with_n_values <- c('same_country', 'prs_pri_same_nationality')

# Create a logical mask to identify rows with '\\N' in any of the specified columns
mask <- apply(df_nonmerged_encoded[columns_with_n_values], 1, function(row) any(grepl('\\N', row)))

# Use the mask to filter and display the rows where '\\N' occurs
rows_with_n_values <- df_nonmerged_encoded[mask, ]

# Replace '\\N' values with 0 in the selected columns
for (column in columns_with_n_values) {
  df_nonmerged_encoded[[column]][df_nonmerged_encoded[[column]] == '\\N'] <- 0
}


```

formula <- manual_analysis ~ status + comments_counts (1) + commit_counts(0) + code_changes_counts(0) + author_country(0) + closer_country(0) + author_continent(1) + same_country(1) + author_eth(1) + closer_eth() + same_eth(۱) + prs_white() + prs_api() + prs_black() + prs_hispanic() + pri_white() + pri_black() + pri_api() + pri_hispanic() + prs_eth_8() + prs_eth_7() + prs_eth_9() + prs_eth_diff() + prs_eth_diff_2() + manual_analysis() + prs_experience(0) + prs_succ_rate(0) + prs_popularity(0) + prs_watched_repo(0) + prs_followed_pri(0) + prs_tenure_mnth(0) + prs_main_team_member() + (1 | author_id)

```{r}
formula <- manual_analysis ~ comments_counts + comments_counts + commit_counts + code_changes_counts + author_country + closer_country + author_continent + same_country + author_eth + closer_eth + same_eth  + prs_experience + prs_succ_rate + prs_popularity + prs_watched_repo + prs_followed_pri + prs_tenure_mnth + prs_main_team_member+  (1 | repo_id) + (1 | author_id)
model <- glmer(formula, data = df_nonmerged_encoded, family = binomial, glmerControl(optCtrl=list(maxfun=2e8)))

```

```{r}
summary(model)
```

```{r}
colSums(is.na(df_nonmerged_encoded))
```


# Building the model for all merged and nonmerged pull reqests
this would be based on status of the pull request

## Encoding the model

```{r}
# Create a copy of df_nonmerged
df_comp_encoded <- df_comp

# Define encoding for 'manual_analysis' column
encoding <- c(
  'Quality' = 0, 'Successful' = 0, 'Unnecessary' = 1, 'No reason' = 0,
  'Resolved' = 0, 'Replaced' = 0, 'Duplicate' = 0, 'Stale' = 0,
  'Merge Conflict' = 0, 'Chaotic' = 0, 'Not PR' = 0
  
)

# Map the encoding to 'manual_analysis' and convert to integer
#df_nonmerged_encoded$manual_analysis <- as.integer(factor(df_nonmerged_encoded$manual_analysis, levels = names(encoding)))
#df_nonmerged_encoded$manual_analysis <- encoding[df_nonmerged_encoded$manual_analysis]

# Replace missing values with 0 in selected columns
df_comp_encoded[is.na(df_comp_encoded)] <- 0

# Encode categorical columns using forcats
categorical_cols <- c(
  'author_id', 'author_eth', 'author_country', 'author_continent',
  'closer_eth', 'prs_eth_8', 'prs_eth_7', 'prs_eth_9',
  'prs_eth_diff', 'prs_eth_diff_2', 'closer_country'
)

for (col in categorical_cols) {
  df_comp_encoded[[col]] <- as.integer(factor(df_comp_encoded[[col]]))
}
# encoding status as zero for merged and 1 for not-merged
df_comp_encoded$status <- ifelse(df_comp_encoded$status == "merged", 0, 1)


```
## remove the \\N values and change them with 0
```{r}
# Define the columns with '\\N' values
columns_with_n_values <- c('same_country', 'prs_pri_same_nationality')

# Create a logical mask to identify rows with '\\N' in any of the specified columns
mask <- apply(df_comp_encoded[columns_with_n_values], 1, function(row) any(grepl('\\N', row)))

# Use the mask to filter and display the rows where '\\N' occurs
rows_with_n_values <- df_comp_encoded[mask, ]

# Replace '\\N' values with 0 in the selected columns
for (column in columns_with_n_values) {
  df_comp_encoded[[column]][df_comp_encoded[[column]] == '\\N'] <- 0
}


```

sampling the data to time the model and see if this works
```{r}
df_comp_encoded_sample <- df_comp_encoded %>% sample_n(1000) 
```
also normalizing to see what is the problem
```{r}
df_comp_encoded_sample <- df_comp_encoded_sample %>% mutate_at(vars(code_changes_counts, author_country, closer_country, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_tenure_mnth ), scale)

```

formula <- status ~ comments_counts + commit_counts + code_changes_counts + author_country + closer_country + author_continent + same_country<> + author_eth + closer_eth + same_eth<>  + prs_experience + prs_succ_rate + prs_popularity + prs_watched_repo + prs_followed_pri <> + prs_tenure_mnth + prs_main_team_member <>+  (1 | repo_id) + (1 | author_id)

```{r}
#formula <- status ~ comments_counts + commit_counts + author_continent  + author_eth + closer_eth  +  (1 | repo_id) 
formula <- status ~ comments_counts + commit_counts + code_changes_counts + author_country + closer_country + author_continent  + author_eth + closer_eth  + prs_experience + prs_succ_rate + prs_popularity + prs_watched_repo + prs_tenure_mnth +  (1 | repo_id) + (1 | author_id)
model <- glmer(formula, data = df_comp_encoded_sample, family = binomial, glmerControl( optCtrl = list(maxfun=1e8)))

```

```{r}
summary(model)
```





# Building the model in rejected categories with samples of nonmerged
## Sampling the Data from merged prs based on nonmerged prs rejection reasons

```{r}
category <- 'Unnecessary'

# Calculate the desired number of samples for the specified category
number_of_samples <- sum(df_nonmerged$manual_analysis == category)

# Filter repo_id values associated with the specified category in df_nonmerged
repo_ids_for_category <- unique(df_nonmerged[df_nonmerged$manual_analysis == category, ]$repo_id)

# Filter 'df_merged' to keep only rows with 'repo_id' values in repo_ids_for_category
filtered_df_merged <- df_merged[df_merged$repo_id %in% repo_ids_for_category, ]

# Create an empty data frame to store the sampled data
sampled_data <- data.frame()

# Iterate through the repositories with rejected PRs in the specified category
for (repo_id in repo_ids_for_category) {
  # Filter rows from filtered_df_merged for the current repo_id
  repo_samples <- filtered_df_merged[filtered_df_merged$repo_id == repo_id, ]
  
  # If there are multiple samples for the current repo, select one randomly
  if (nrow(repo_samples) > 1) {
    set.seed(42)  # Set seed for reproducibility
    repo_samples <- repo_samples[sample(nrow(repo_samples), size = 1), ]
  }
  
  # Append the selected sample to the sampled_data data frame
  sampled_data <- rbind(sampled_data, repo_samples)
}

# Randomly select additional samples to reach the desired number
remaining_samples <- number_of_samples - nrow(sampled_data)
set.seed(42)  # Set seed for reproducibility
additional_samples <- filtered_df_merged[sample(nrow(filtered_df_merged), size = remaining_samples), ]

# Append the additional samples to the sampled_data data frame
sampled_data <- rbind(sampled_data, additional_samples)
```
checking to see if the repos are the same
```{r}
# Get the unique 'repo_id' values from the sampled_data data frame
sampled_repo_ids <- unique(sampled_data$repo_id)

# Check if all sampled 'repo_id' values are in 'repo_ids_for_category'
if(all(sampled_repo_ids %in% repo_ids_for_category)) {
  cat("All samples are from repositories with the specified rejected reason.\n")
} else {
  cat("Some samples are not from repositories with the specified rejected reason.\n")
}
```

```{r}
# there is a closer_id feature in sample_reason that is not in nonmerged, let's drop that first
sampled_data <- sampled_data[, !(names(sampled_data) %in% "closer_id")]
sampled_data <- sampled_data[, !(names(sampled_data) %in%  "checked")]

```



```{r}

common_columns <- intersect(names(df_nonmerged), names(sampled_data))
sampled_data <- sampled_data %>% rename(!!!setNames(common_columns, common_columns))
df_nonmerged_category <- df_nonmerged[df_nonmerged$manual_analysis == category, ]
df_nonmerged_category <- df_nonmerged_category[, !(names(df_nonmerged_category) %in% "manual_analysis")]


# Concatenate data frames df_nonmerged and sampled_data by rows
df_sample_reason <- rbind(df_nonmerged_category, sampled_data) 


# Sort the resulting data frame by 'repo_id'
df_sample_reason <- df_sample_reason[order(df_sample_reason$repo_id), ]

# Drop the 'checked' and 'manual_analysis' columns
df_sample_reason <- df_sample_reason[, !(names(df_sample_reason) %in% c('checked', 'manual_analysis'))]

```

```{r}
table(df_sample_reason$status)

```

