---
title: "Comparing_models"
output: html_document
date: "2023-09-18"
---

```{r}
library(readr)
library(dplyr)
library(forcats)
library(lme4)

```

```{r}
df_nonmerged <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/Non_Merged/Sample/temp/Sample_10000_manual.csv")
df_merged <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/Merged/pr_merged_final_April_2023.csv")
df_comp <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Dataset/pr_final_April_2023.csv")
df_TSE <- read_csv("/Users/amirrshams/Library/CloudStorage/OneDrive-UniversityofWaterloo/Thesis/Dataset/Reza's Dataset/TSE paper/2020-TSE-Developers-Perceptible-Ethnicity-and-PR-evaluation-main/Dataset/pull_requests.csv")
```

```{r}
df_TSE <- df_TSE %>%
  distinct(pr_id, .keep_all = TRUE)

df_nonmerged <- df_nonmerged %>%
  distinct(pr_id, .keep_all = TRUE)
```

```{r}
df_nonmerged <- left_join(df_nonmerged, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)
```

```{r}
df_merged <- left_join(df_merged, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)

df_comp <- left_join(df_comp, select(df_TSE, pr_id, prs_pri_same_nationality, prs_experience, prs_succ_rate, prs_popularity, prs_watched_repo, prs_followed_pri, prs_tenure_mnth, prs_main_team_member)
, by= "pr_id", all.y = TRUE)
```

```{r}
df_nonmerged <- df_nonmerged %>%
  select(-c(`Unnamed: 0`, pr_id, pullreq_id, api_url, url, pr_url, pr_api_url, author_desc_body, closer_id, comments, created_at, closed_at))


df_merged <- df_merged %>%
  select(-c(`Unnamed: 0`, pr_id, pullreq_id, api_url, url, pr_url, pr_api_url, author_desc_body, closer_id, comments, created_at, closed_at))


df_comp <- df_comp %>%
  select(-c(`Unnamed: 0`, pr_id, pullreq_id, api_url, url, pr_url, pr_api_url, author_desc_body, closer_id, comments, created_at, closed_at))

```


```{r}
# Create a copy of df_nonmerged
df_nonmerged_encoded <- df_nonmerged

# Define encoding for 'manual_analysis' column
encoding <- c(
  'Quality' = 0, 'Successful' = 0, 'Unnecessary' = 1, 'No reason' = 0,
  'Resolved' = 0, 'Replaced' = 0, 'Duplicate' = 0, 'Stale' = 0,
  'Merge Conflict' = 0, 'Chaotic' = 0, 'Not PR' = 0
)

# Map the encoding to 'manual_analysis' and convert to integer
df_nonmerged_encoded$manual_analysis <- as.integer(factor(df_nonmerged_encoded$manual_analysis, levels = names(encoding)))
df_nonmerged_encoded$manual_analysis <- encoding[df_nonmerged_encoded$manual_analysis]

# Replace missing values with 0 in selected columns
df_nonmerged_encoded[is.na(df_nonmerged_encoded)] <- 0

# Encode categorical columns using forcats
categorical_cols <- c(
  'author_eth', 'author_country', 'author_continent',
  'closer_eth', 'prs_eth_8', 'prs_eth_7', 'prs_eth_9',
  'prs_eth_diff', 'prs_eth_diff_2', 'closer_country', 'status'
)

for (col in categorical_cols) {
  df_nonmerged_encoded[[col]] <- as.integer(factor(df_nonmerged_encoded[[col]]))
}

```

```{r}
table(df_nonmerged_encoded$manual_analysis)
```
```{r}
# Define the columns with '\\N' values
columns_with_n_values <- c('same_country', 'prs_pri_same_nationality')

# Create a logical mask to identify rows with '\\N' in any of the specified columns
mask <- apply(df_nonmerged_encoded[columns_with_n_values], 1, function(row) any(grepl('\\N', row)))

# Use the mask to filter and display the rows where '\\N' occurs
rows_with_n_values <- df_nonmerged_encoded[mask, ]

# Replace '\\N' values with 0 in the selected columns
for (column in columns_with_n_values) {
  df_nonmerged_encoded[[column]][df_nonmerged_encoded[[column]] == '\\N'] <- 0
}


```

formula <- manual_analysis ~ status + comments_counts (1) + commit_counts(0) + code_changes_counts(0) + author_country(0) + closer_country(0) + author_continent(1) + same_country(1) + author_eth(1) + closer_eth() + same_eth(۱) + prs_white() + prs_api() + prs_black() + prs_hispanic() + pri_white() + pri_black() + pri_api() + pri_hispanic() + prs_eth_8() + prs_eth_7() + prs_eth_9() + prs_eth_diff() + prs_eth_diff_2() + manual_analysis() + prs_experience(0) + prs_succ_rate(0) + prs_popularity(0) + prs_watched_repo(0) + prs_followed_pri(0) + prs_tenure_mnth(0) + prs_main_team_member() + (1 | author_id)

```{r}
formula <- manual_analysis ~ comments_counts  + author_continent + same_country + author_eth + closer_eth + same_eth + (1 | author_id)
model <- glmer(formula, data = df_nonmerged_encoded, family = binomial)

```

```{r}
summary(model)
```

```{r}
colSums(is.na(df_nonmerged_encoded))
```

